Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/discussion.tex
add discussion input to main tex
get started with discussion

Discuss points (still need to check results, to see we haven't left some of this there):

@@

- The far right peak is probably because of 3D EFFECTS, the second peak, in the original runs, it was definitely related to the the 
sharp edges since when we introduce a level of roundness, it disappear. The peaks wavelength match perfectly, as seen in the Figure 
\ref{{fig:rep_14}}. We can say we replicate this result. 
Challenges: all what's on the replication list that should go in the background

>>>>

%!TEX root = ClementiBarba2020.tex

We have presented several results that replicate previous published findings in the general area of nanostructure responses to electromagnetic waves. 
Our field of interest is computational nanoplasmonics for applications in biosensors, and in a previous publication we developed the mathematical formulation and reported both solution verification activities, and an application demo with our software \pygbe, extended to treat complex dielectrics.
The search for a physical context and published results that would allow us to undertake validation studies with \pygbe is what led us to this work. 
Even if we finally do have validation and replication cases, neatly presented here, the path to obtain these results was nonlinear, iterative, and arduous.

In the first case, we sought to replicate a result from Rockstuhl et al., 2005 \cite{rockstuhl2005} where they computed the scattering cross-section as a function of wavelength for a silicon carbide nanostructure. 
They present their results as a plot, and report the numeric value of the resonance wavelength in the text. 
Lacking access to the secondary data behind the plots---computed from two-dimensional simulations with a boundary element solver---we were forced to manually digitize the values from the figure.
Our results are presented in Figure \ref{fig:rep_14}, together with the curve we obtain from digitizing the source image.

@@

- The far right peak is probably because of 3D EFFECTS, the second peak, in the original runs, it was definitely related to the the 
sharp edges since when we introduce a level of roundness, it disappear. The peaks wavelength match perfectly, as seen in the Figure 
\ref{fig:rep_14}. We can say we replicate this result. 
Challenges: all what's on the replication list that should go in the background

### 2020-07-26 tex/results.tex
use dip for inverted peak
get started with discussion

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
closely matched. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}

@@

\paragraph{Method:}
Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
In their simulations, 
they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in this case 
since the pillar's size is small compared to the wavelengths involved in the simulations: 
which are in the range 10000--12500 nm. 
We measure extinction cross section, which will express as peaks instead of depressions (shown in the reflection plots of Ellis et al.). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
the aspect ratio variation study.

>>>>

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by hand using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
closely matched. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl et al.\ 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}

@@

\paragraph{Method:}
Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
In their simulations, 
they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in this case 
since the pillar's size is small compared to the wavelengths involved in the simulations: 
which are in the range 10000--12500 nm. 
We measure extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per Angstrom-squared to create the meshes for 
the aspect ratio variation study.
